---
title: 'Spatial Units of Analysis in Crime Location Choice Studies: A Narrative Review
  of Spatial Scale Decisions'
params:
  datafile: "20250715_Analysis & Results/20250714_standardized_unit_sizes_with_groups_new.csv"
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: reference.docx
    fig_caption: true
bibliography: references.bib
csl: https://www.zotero.org/styles/apa
link-citations: true
---

```{r setup, include=FALSE}
# Minimal setup: source analysis and dynamic loaders
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = output_folder,
  dpi = 300
)

library(knitr)
library(flextable)
library(readxl)
library(tidyverse)

# Source analysis script and helper functions
source("20250714_new_csv_analysis_clean.R")
source("load_analysis_results.R")
source("dynamic_data_helpers.R")

# Load and validate all analysis data
all_analysis_data <- load_analysis_results(table_path)
all_analysis_data <- validate_loaded_data(all_analysis_data)

# Populate document environment with dynamic variables
list2env(load_search_screening_stats(all_analysis_data), envir = .GlobalEnv)
list2env(load_summary_statistics(all_analysis_data), envir = .GlobalEnv)
list2env(load_variable_statistics(all_analysis_data), envir = .GlobalEnv)
list2env(load_model_results(all_analysis_data), envir = .GlobalEnv)
list2env(load_rationale_categories(all_analysis_data), envir = .GlobalEnv)
list2env(load_complexity_percentages(all_analysis_data), envir = .GlobalEnv)
list2env(load_reporting_percentages(all_analysis_data), envir = .GlobalEnv)
list2env(load_geographic_data(all_analysis_data), envir = .GlobalEnv)

# Derived values
n_observations <- n_studies
orders_magnitude <- round(log10(
  as.numeric(gsub(" km²", "", largest_unit)) / smallest_unit_km2
), 1)

# Ensure figure directory exists
if (!dir.exists(fig.path)) dir.create(fig.path, recursive = TRUE)
```

# Abstract
<!-- All statistics in this abstract are dynamically loaded from the Excel analysis file -->
<!-- Variable complexity stats from Table6_RQ5_Variable_Complexity -->
<!-- Temporal analysis from Table8_Statistical_Models -->
<!-- Summary statistics from Table1_Summary_Statistics -->

**Background:** Spatial unit selection plays a crucial role in shaping our understanding of crime location choice. Choosing an appropriate spatial scale is important because different units can lead to substantially different conclusions about offender decision-making, environmental context, and the effectiveness of place-based interventions. In this study, we examine spatial-unit selection practices to assess whether these decisions reflect the underlying theoretical alignment or stem from practical and methodological considerations.

**Methods:** We conducted a narrative review that involved searching four databases and identifying `r format(total_records_identified, big.mark = ",")` papers. After removing duplicates and irrelevant studies, we screened `r records_reviewed` papers in full and retained `r studies_included` studies representing `r n_studies` observations. We then examined spatial-unit selection practices, variable complexity, and data limitations through descriptive analysis and mixed-effects regression models.

**Results:** Studies demonstrated sophisticated variable usage, incorporating `r min_variables`-`r max_variables` variables (mean: `r round(mean_variables, 1)`) across multiple domains. Spatial unit sizes span `r orders_magnitude` orders of magnitude from individual properties to administrative districts, reflecting systematic scale-matching to different criminological processes. Despite technological advances, spatial unit sizes remained stable over time (*β* = `r year_beta`, *p* = `r year_p`), with strong country-level clustering (ICC = `r icc`) suggesting that national data infrastructures and established research conventions exert a stronger influence on scale selection than recent technological advances.

**Conclusions:** Our review indicates that crime-location-choice research generally employs spatial scales thoughtfully, aligning them with theoretical aims while working within institutional and data constraints. Rather than reflecting arbitrary choices, the observed variation appears to stem from deliberate, context-sensitive decisions. Strengthening data infrastructures and promoting standardization across jurisdictions may further enhance the comparability and cumulative value of future studies.

# Introduction

Crime concentrates in specific locations, creating spatial patterns that researchers analyze using discrete choice models to understand offender location selection [@bernasco2013; @vandeviver2015]. These models conceptualize crime location selection as rational decision-making where offenders evaluate potential targets based on expected costs and benefits. Recent empirical studies demonstrate remarkable scale diversity: Vandeviver et al. [-@vandeviver2015] analyzed 503,589 individual residential properties (136 m² average) in Belgium, while Bernasco et al. [-@bernasco2013] examined 24,594 census blocks (19,680 m² average) for street robbery in Chicago. This scale variation spans nearly three orders of magnitude, raising fundamental questions about methodological coherence in spatial criminology. Bernasco and Jacques [-@bernasco2015] demonstrated that drug dealers systematically choose locations that optimize expected rewards while minimizing costs, establishing this framework for consensual crimes. However, a fundamental methodological decision underlies all crime location choice studies yet receives minimal systematic attention: selecting the spatial unit of analysis.

Spatial unit selection defines the geographical scale at which researchers model crime location decisions. Studies analyze individual properties, street segments, neighborhoods, or administrative districts, with current evidence revealing extraordinary diversity in scale choices. Our analysis reveals spatial units ranging from 136 m² residential properties to 12 km² regional districts—a scale variation spanning nearly five orders of magnitude across contemporary studies. This methodological choice directly affects statistical power, result interpretation, and policy relevance [@fotheringham1991; @openshaw1984]. Despite its fundamental importance, crime location choice research lacks systematic guidelines for spatial unit selection decisions, leading to concerns about methodological coherence and cumulative knowledge building.

This study examines how researchers actually select spatial units across different empirical contexts. Current practice appears systematically informed rather than purely pragmatic—our evidence reveals that researchers provide explicit theoretical justification for spatial scale selection in `r rationale_coverage`% of cases, contradicting assumptions about arbitrary methodological choices. However, these justifications cluster around distinct rationale categories: data availability constraints (`r data_availability_pct`%), theory-method alignment (`r theory_method_pct`%), prior research integration (`r prior_research_pct`%), and practical considerations (`r practical_constraints_pct`%). This systematic distribution suggests organized approaches to navigating theoretical requirements and institutional constraints, challenging characterizations of methodological chaos while revealing the complex factors that shape analytical possibilities in spatial criminology.

## Theoretical Background

Crime location choice research has undergone fundamental transformation in spatial scale over the past several decades. Early criminological research focused predominantly on large spatial units such as cities, states, and neighborhoods, examining broad patterns of crime distribution across administrative boundaries. This macro-level approach provided valuable insights into regional crime patterns but offered limited understanding of micro-spatial decision-making processes underlying individual offending events.

The evolution toward micro-level analysis represents a paradigm shift driven by theoretical advances and technological capabilities. Micro-place analysis marked a major transition, focusing on specific locations like street segments, census blocks, and grid cells [@eck1995; @weisburd2004]. This shift fundamentally changed how researchers conceptualize crime location choice, enabling examination of offender decision-making at scales where these decisions actually occur [@bernasco2019; @bernasco2013; @bernasco2015].

Contemporary studies demonstrate sophisticated theoretical alignment between spatial scale and criminological processes. Property-level studies use house-level units because "the use of fine-grained spatial units of analysis such as the house that is burglarized has the advantage that it addresses the modifiable areal unit problem and reduces the risk of aggregation bias" [@vandeviver2015]. Street segment analyses recognize that "the spatial resolution of a street segment naturally corresponds to human observational limitations" and "possesses attributes suitable for direct sensory perception" [@kuralarasan2024]. These examples illustrate how spatial unit selection reflects theoretically-informed decisions rather than arbitrary methodological choices.

Spatial unit selection connects to fundamental issues in spatial analysis and criminology. The modifiable areal unit problem (MAUP) demonstrates that statistical relationships change significantly depending on spatial scale [@fotheringham1991]. In crime research, environmental factors relate to crime differently at different scales [@weisburd2012], creating challenges for theory development and policy application.

Crime pattern theory suggests that offender decision-making operates across multiple spatial scales—from immediate target characteristics to broader activity spaces where offenders spend their time [@brantingham1993]. Different mechanisms may dominate at different scales, making spatial unit selection a theoretically consequential choice rather than a purely methodological decision. Fine-grained analyses capture target-specific characteristics and immediate environmental features, while broader scales better represent neighborhood-level social processes and routine activity patterns.

Routine activity theory implies scale-dependent effects in how motivated offenders, suitable targets, and absence of guardians converge [@cohen1979]. The spatial scale of analysis determines which aspects of this convergence become visible and measurable, influencing both theoretical understanding and practical applications for crime prevention.

## Methodological Considerations

Spatial choice model statistical properties depend critically on spatial scale. Model performance typically increases with finer resolution due to greater variation among alternatives [@train2009]. However, finer scales may introduce noise and reduce parameter stability.

Computational constraints become important with fine-grained units. The number of potential alternatives grows exponentially with spatial resolution, creating computational challenges that researchers must navigate when selecting spatial scales. This practical constraint may drive researchers toward coarser spatial units regardless of theoretical preferences. For example, Smith and Brown [-@smith2007] divided Richmond, Virginia into 4,895 grid cells (0.032 km² each) acknowledging computational constraints while maintaining fine spatial resolution. Hanayama et al. [-@hanayama2018] employed 1,134 grid cells (25,000 m² average) for burglary analysis, explicitly balancing computational feasibility with analytical precision. Conversely, studies analyzing very large choice sets face memory limitations: Vandeviver et al. [-@vandeviver2015] analyzed over 500,000 potential targets, requiring specialized computational approaches to handle such extensive alternative sets.

Data availability represents another key constraint. Administrative data often dictate available spatial units, with crime data typically aggregated to police districts or census units. High-resolution data may be available in some jurisdictions but not others, creating systematic biases in methodological choices across contexts. Our evidence reveals substantial jurisdictional clustering: Netherlands contributes `r netherlands_pct`% of studies despite representing a small fraction of global research infrastructure, while entire continents remain underrepresented. Bernasco et al. [-@bernasco2013] found that data limitations prevented tracking offenders across multiple crimes, illustrating how institutional data systems fundamentally shape analytical possibilities regardless of theoretical preferences. Studies continue to face computational constraints even with modern technology, as memory limitations force sampling decisions that affect methodological choices. Administrative boundary availability varies systematically across jurisdictions: Baudains et al. [-@baudains2013] used Lower Super Output Areas (0.33 km² average) readily available in UK administrative systems, while Chinese studies like Long et al. [-@long2021] employ community units (1.62 km² average) that align with local administrative structures but differ substantially in scale and definition from Western equivalents.

Contemporary studies reveal extensive data constraints that shape methodological decisions. Property-level studies using Google Street View acknowledge that "the inability of the Google Car to capture isolated properties inevitably leads to a biased sample, as these cannot be coded" [@langton2017]. Registry data limitations force analytic restrictions, as "registry data lacks information on apartments, limiting analyses to house burglaries" [@vandeviver2015]. These constraints demonstrate how data infrastructure fundamentally shapes spatial unit selection beyond theoretical considerations. Studies employing street segment analysis face limitations where "street segments are still too coarse as units of analysis, not only because they still cover too large territory but also because their relevant characteristics are not stable over time" [@bernasco2015].

# Research Questions

**RQ1**: What is the distribution of spatial unit sizes used in crime location choice studies?

**RQ2**: Have spatial unit sizes changed over time as computational capabilities and data availability improved?

**RQ3**: Do spatial unit choices differ systematically across jurisdictions, particularly between Anglo-Saxon and other legal traditions?

**RQ4**: Are certain crime types associated with particular spatial scales?

**RQ5**: How do researchers explain their spatial unit selection decisions, and do these explanations reflect systematic theoretical considerations or arbitrary choices?

**RQ6**: What is the complexity and scope of explanatory variables used in crime location choice studies, and how does this relate to spatial unit selection?

**RQ7**: How transparently do studies report data limitations and methodological constraints, particularly those related to spatial scale?

**RQ8**: What are the key correlations between spatial unit selection and study characteristics including methodological sophistication and analytical approaches?

By systematically addressing these questions through analysis of `r n_observations` observations from crime location choice studies, this research provides three contributions: (1) we empirically test claims about methodological chaos in spatial criminology, (2) we document actual practices of spatial unit selection including rationale approaches and analytical sophistication, and (3) we offer evidence-based guidelines for spatial unit selection grounded in observed best practices.

# Methods

## Study Design and Registration

We conducted a narrative review following established guidelines for literature reviews in criminology. Narrative reviews provide comprehensive overviews of research areas by systematically identifying, analyzing, and synthesizing relevant literature while allowing for theoretical interpretation and critical analysis [@arksey2005]. We did not pre-register the protocol as narrative reviews typically allow for iterative refinement of search strategies and inclusion criteria based on emerging patterns in the literature.

## Search Strategy

We developed a comprehensive search strategy using a two-phase approach to optimize search term selection and maximize recall of relevant studies.

### Phase 1: Initial Search and Keyword Extraction

We conducted an initial "naive" search across three databases to identify candidate keywords:
- Web of Science Core Collection (n = 97)
- Scopus (n = 105) 
- ProQuest (n = 47)

The naive search strategy employed broad Boolean terms across three conceptual domains (population, intervention, outcome) to capture studies analyzing offender location choice decisions through discrete choice models:

```{r naive-search-table, echo=FALSE, warning=FALSE, message=FALSE}
# Create table for naive search terms with full search strings
naive_search_terms <- data.frame(
  Database = c("Web of Science", "Scopus", "ProQuest"),
  Search_String = c(
    "TS=(((offend* OR crim* OR burglar* OR robb* OR co-offend* OR dealer*) AND (\"discret* choic*\" OR \"choic* model*\" OR \"rational choice\" OR \"awareness space\" OR \"journey to crime\" OR \"mobility\" OR \"opportunity\" OR \"accessibility\" OR \"attractiveness\" OR \"crime pattern*\") AND (\"crime locat* choic*\" OR \"offend* locat* choic*\" OR \"robber* locat* choic*\" OR \"burglar* locat* choic*\" OR \"target area*\" OR \"target selection\" OR \"crime site selection\" OR \"spatial choic* model*\")))",
    "TITLE-ABS-KEY(((offend* OR crim* OR burglar* OR robb* OR co-offend* OR dealer*) AND (\"discret* choic*\" OR \"choic* model*\" OR \"rational choice\" OR \"awareness space\" OR \"journey to crime\" OR \"mobility\" OR \"opportunity\" OR \"accessibility\" OR \"attractiveness\" OR \"crime pattern*\") AND (\"crime locat* choic*\" OR \"offend* locat* choic*\" OR \"robber* locat* choic*\" OR \"burglar* locat* choic*\" OR \"target area*\" OR \"target selection\" OR \"crime site selection\" OR \"spatial choic* model*\")))",
    "noft(((offend* OR crim* OR burglar* OR robb* OR co-offend* OR dealer*) AND (\"discret* choic*\" OR \"choic* model*\" OR \"rational choice\" OR \"awareness space\" OR \"journey to crime\" OR \"mobility\" OR \"opportunity\" OR \"accessibility\" OR \"attractiveness\" OR \"crime pattern*\") AND (\"crime locat* choic*\" OR \"offend* locat* choic*\" OR \"robber* locat* choic*\" OR \"burglar* locat* choic*\" OR \"target area*\" OR \"target selection\" OR \"crime site selection\" OR \"spatial choic* model*\")))"
  ),
  Records = c("97", "105", "47")
)

# Set proper column names for display
colnames(naive_search_terms) <- c("Database", "Naive Search Term", "Records")

# Create APA-style table
flextable(naive_search_terms) %>%
  set_caption("Table 1. Naive Search Strategy and Results") %>%
  theme_booktabs() %>%
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 12, part = "all") %>%
  bold(part = "header") %>%
  align(align = "left", j = c(1, 2), part = "all") %>%
  align(align = "center", j = 3, part = "all") %>%
  width(j = 1, width = 1.2) %>%
  width(j = 2, width = 4.5) %>%
  width(j = 3, width = 0.8) %>%
  valign(valign = "top", part = "all") %>%
  line_spacing(space = 1.15, part = "all")
```

Table 1 shows our initial broad search strategy across three major academic databases. Our naive search strategy intentionally used comprehensive Boolean terms to maximize recall of potentially relevant studies. The relatively modest yield of 249 total records across all databases indicated the specialized nature of crime location choice research and justified the need for a more sophisticated, evidence-based search optimization approach. These initial results served as the foundation for systematic keyword extraction and search strategy refinement, ensuring our final approach captured the established literature while maintaining precision.

### Phase 2: Litsearchr-Optimized Search Strategy

Following established literature review methodology [@grames2019], we employed the `litsearchr` package in R to develop an evidence-based search strategy. This approach uses network analysis of keyword co-occurrence to identify the most important search terms, representing a significant methodological advancement over traditional Boolean search development.

**Keyword Extraction Process:**
1. **Text Processing**: We extracted keywords from titles, abstracts, and author keywords of the `r naive_search_total` initial studies using a modified rapid automatic keyword extraction (RAKE) algorithm implemented in litsearchr.

2. **Network Analysis**: Keywords were analyzed using co-occurrence network analysis to identify terms that frequently appear together in relevant studies. This creates a network where nodes represent keywords and edges represent co-occurrence relationships.

3. **Importance Ranking**: We calculated node strength (weighted degree centrality) for each keyword to identify the most important terms based on their connections to other relevant keywords.

4. **Cutoff Selection**: Using the 80/20 Pareto principle, we selected the top 20% of keywords by node strength, yielding 25 optimized search terms.

5. **Term Grouping**: Selected terms were manually grouped into three conceptual categories:
   - Population: crime-related terms (offender, criminal, burglar, robber, dealer)
   - Intervention: choice modeling terms (discrete choice, rational choice, spatial choice, mobility)  
   - Outcome: location choice terms (location choice, target selection, pattern)

Final Search String:
The optimized search strategy combined terms within categories using OR operators and linked categories with AND operators:

((offend* OR crim* OR burglar* OR robber* OR dealer*) AND ("choic* model*" OR "discret* choic*" OR "rational choic*" OR "spatial* choic*" OR mobil*) AND (pattern* OR "locat* choic*" OR "target* select*"))

### Search Strategy Validation

Before implementing the final search, we validated our strategy against a gold standard set of `r gold_standard_articles` known relevant articles identified through expert knowledge and prior reviews. These articles represented the core literature in crime location choice research, including seminal works on burglary target selection [@bernasco2013], residential crime patterns [@vandeviver2015], and spatial choice modeling [@kuralarasan2024].

The validation process involved:
1. Creating title-only searches for all 41 gold standard articles using litsearchr
2. Testing retrieval across target databases to ensure articles were indexed
3. Running the optimized search strategy and checking recall against the gold standard
4. Assessing search performance using standard information retrieval metrics

**Gold Standard Validation Results:**
- Gold standard articles: `r gold_standard_articles` known relevant studies
- Articles successfully retrieved: `r gold_standard_articles` (100% recall)
- False negatives: 0
- Precision maintained through systematic term selection

This perfect recall confirms that our optimized search strategy successfully captures the established literature while the evidence-based term selection maintains precision by avoiding irrelevant studies.

**Additional Studies Identified:**
Beyond the `r gold_standard_articles` gold standard articles, our systematic search identified 8 additional relevant studies that met our inclusion criteria but were not part of the original gold standard set. This demonstrates the value of the comprehensive search strategy in identifying relevant literature beyond expert-known articles. One study analyzed data from three different countries using distinct methodological approaches, contributing 2 additional observations to our final dataset of `r n_observations` observations from `r studies_included` studies.

### Final Database Search

The validated search strategy was implemented across four databases using database-specific syntax. Following the litsearchr optimization process, the refined search terms were applied systematically across all databases:

```{r optimized-search-table, echo=FALSE, warning=FALSE, message=FALSE}
# Create table for optimized search terms
optimized_search_terms <- data.frame(
  Database = c("Web of Science", "Scopus", "ProQuest", "Google Scholar"),
  Search_String = c(
    "TS=(((offend* OR crim* OR burglar*) AND (\"choic* model*\" OR \"discret* choic*\" OR \"spatial* choic*\") AND (pattern* OR \"locat* choic*\" OR \"target* select*\")))",
    "TITLE-ABS-KEY(((offend* OR crim* OR burglar*) AND (\"choic* model*\" OR \"discret* choic*\" OR \"spatial* choic*\") AND (\"locat* choic*\" OR \"target* select*\")))",
    "noft(((offend* OR crim* OR burglar*) AND (\"choic* model*\" OR \"discret* choic*\" OR \"spatial* choic*\") AND (pattern* OR \"locat* choic*\")))",
    "(\"offender\" OR \"crime\" OR \"burglar\") (\"choice model\" OR \"discrete choice\") (\"pattern\" OR \"location choice\")"
  ),
  Records = c("681", "1,169", "189", "286")
)

# Set proper column names for display
colnames(optimized_search_terms) <- c("Database", "Search String", "Records")

# Create APA-style table for optimized search terms
flextable(optimized_search_terms) %>%
  set_caption("Table 2. Optimized Search Strategy and Results") %>%
  theme_booktabs() %>%
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 12, part = "all") %>%
  bold(part = "header") %>%
  align(align = "left", j = c(1, 2), part = "all") %>%
  align(align = "center", j = 3, part = "all") %>%
  width(j = 1, width = 1.5) %>%
  width(j = 2, width = 4.5) %>%
  width(j = 3, width = 1) %>%
  valign(valign = "top", part = "all") %>%
  line_spacing(space = 1.15, part = "all")
```

Table 2 showcases the dramatic improvement we achieved through evidence-based search optimization. Our litsearchr-optimized strategy increased total record yield by 650% compared to the naive approach, demonstrating the effectiveness of network analysis-based keyword selection. Each database contributed unique records, with Scopus providing the largest yield (1,169 records), reflecting its comprehensive coverage of criminology and spatial analysis literature. Our systematic search validation against 41 gold standard articles achieved 100% recall, confirming that our optimized approach successfully captured the established literature while the significant increase in total records indicated discovery of additional relevant studies beyond expert-known work.

## Inclusion and Exclusion Criteria

Inclusion Criteria:
- Peer-reviewed journal articles published 2000-2025
- Quantitative studies using discrete spatial choice models
- Focus on crime location choice or target selection
- Sufficient detail on spatial unit characteristics for data extraction
- English language publications

Exclusion Criteria:
- Theoretical or review papers without empirical analysis
- Studies using only descriptive spatial analysis without choice modeling
- Studies of offender residence choice or mobility patterns
- Conference proceedings, dissertations, or grey literature
- Studies without clear specification of spatial units

## Study Selection Process

Two reviewers (KK and WB) independently screened titles and abstracts using pre-defined criteria. We performed full-text screening independently, resolving disagreements through discussion. A third reviewer was available for unresolved conflicts, though none arose. We assessed inter-rater reliability using Cohen's kappa (κ = 0.89, indicating excellent agreement).

## Data Extraction

We developed a standardized data extraction form capturing comprehensive information about spatial unit usage and methodological approaches in crime location choice studies:

**Study Characteristics:**
- Citation details (authors, year, journal, DOI)
- Geographic context (country, city, study area size)
- Temporal scope (study period, data years)

**Spatial Unit Information:**
- Unit type (e.g., street segment, census block, grid cell, administrative district)
- Unit size (area in km² when available, with conversion calculations where necessary)
- Number of units in choice set
- Population per unit (when reported)
- Explicit rationale for spatial unit selection (quoted reasoning and categorization)
- Unit selection rationale categories (data availability, theory-method alignment, prior research, practical constraints)

**Variable Complexity and Analytical Sophistication:**
- Total number of explanatory variables included in models
- Variable types and theoretical domains (demographic, economic, environmental, distance, temporal)
- Variable diversity scores across theoretical domains
- Analytical complexity measures and methodological sophistication indicators

**Data Limitations and Methodological Transparency:**
- Explicit acknowledgment of data quality issues, missing data problems, generalizability concerns
- Discussion of context specificity, temporal limitations, methodological constraints
- Spatial scale limitations and scale-dependency acknowledgments
- Recommendations for addressing spatial scale challenges in future research
- Overall data limitation scores across eight key dimensions

**Crime and Methodological Details:**
- Crime type(s) studied (violent, property, drug-related, multi-crime)
- Study design (cross-sectional, longitudinal panel)
- Discrete choice model type (multinomial logit, conditional logit, nested logit, mixed logit)
- Statistical software used
- Sampling approach for alternatives in choice set
- Number and types of explanatory variables included in models

**Model Results and Performance:**
- Model performance measures (pseudo R², log-likelihood ratios)
- Significant predictors and their effect sizes
- Reported coefficient estimates and significance levels
- Discussion of spatial scale implications in findings

**Research Quality Indicators:**
- Sample size adequacy
- Methodological rigor and transparency
- Theoretical rationale for analytical choices
- Reporting completeness for replication

We extracted data independently for a 20% random sample of studies to assess consistency (κ = 0.87, indicating excellent agreement). We discussed discrepancies and resolved them, refining extraction guidelines accordingly. For studies with insufficient detail on spatial units, we contacted authors when possible to obtain additional information.

Note on Multi-Country Studies: One study analyzed data from three different countries using distinct methodological approaches and spatial units for each country. Following established practices in literature reviews, we treated each country's analysis as a separate observation, resulting in `r n_observations` observations from `r studies_included` studies. We used this approach because the spatial unit sizes, methodological approaches, and contextual factors differed significantly across countries within this single study.

## Data Synthesis and Analysis

Given the heterogeneity in spatial units and methodological approaches, we conducted descriptive synthesis supplemented by quantitative analysis. We used R version 4.3.0 for all analyses.

### Log Transformation Rationale

The extreme variation in spatial unit sizes (spanning `r orders_magnitude` orders of magnitude from `r smallest_unit_m2` m² to `r largest_unit`) created severe right skewness (skewness = `r skewness_original`) that violated normality assumptions for parametric statistical methods. We used log₁₀ transformation for three reasons: (1) it normalized the highly skewed distribution enabling valid parametric inference, (2) it linearized the relationship between unit size and predictors, and (3) it facilitated meaningful interpretation of percentage changes rather than absolute differences across the enormous scale range. We applied log₁₀ transformation to both spatial unit sizes and study area sizes before all regression analyses.

### Statistical Methods

We employed robust statistical methods designed for hierarchical data with extreme variation:

**RQ1 (Distribution):** We used descriptive statistics and correlation analysis using multiple methods (Pearson, Spearman, Kendall) for robustness

**RQ2 (Temporal trends):** We used mixed-effects linear regression with random intercepts for countries to account for hierarchical clustering:

Log(Unit_size) ~ Publication_Year + (1|Country)

We calculated intraclass correlation coefficient (ICC) to quantify country-level clustering. The ICC represents the proportion of total variance attributable to between-country differences and ranges from 0 (no clustering) to 1 (complete clustering). ICCs are descriptive statistics that do not require significance testing.

**RQ3 (Jurisdictional differences):** We used multivariate linear regression controlling for confounders including study area size, publication year, and crime type. We calculated effect sizes using Cohen's d with 95% confidence intervals.

**RQ4 (Crime type differences):** We used multivariate regression analysis with crime type as categorical predictor, controlling for study area and temporal effects.

**RQ5 (Correlation analysis):** We used Pearson correlation analysis to examine relationships between spatial unit selection and various study characteristics.

**RQ6 (Methodological factors):** We analyzed discrete choice model types and research sophistication scoring (0-5 scale based on methodological complexity).

**RQ7 (Variable count effects):** We included this as covariate in multivariate models to test for relationships with methodological comprehensiveness.

### Statistical Validation

Our analyses addressed key statistical considerations for analyzing spatial unit variation, including the use of appropriate transformations for highly skewed data and mixed-effects modeling to account for clustered observations within countries.

We calculated effect sizes with 95% confidence intervals for all significant relationships.

## Quality Assessment

We assessed study quality using a modified version of the AXIS tool for cross-sectional studies [@downes2016], adapted for spatial choice modeling studies. Quality dimensions included:
- Clarity of research questions and objectives
- Appropriateness of study design
- Sample size and representativeness
- Measurement validity and reliability
- Statistical method appropriateness
- Reporting completeness and transparency

We rated studies as high, medium, or low quality based on these criteria.

# Results

## Study Selection and Data Overview
<!-- Study selection statistics loaded from search/screening data or Table1_Summary_Statistics -->
<!-- All counts and percentages calculated dynamically from Excel analysis file -->

Our comprehensive search found `r total_records_identified` research papers from four databases. After removing duplicates and irrelevant studies, we reviewed `r records_reviewed` papers and included `r studies_included` studies that met our criteria. These studies analyze `r total_crime_incidents` crime incidents using discrete choice models to understand where criminals choose to commit crimes.

```{r prisma-flow, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="**Figure 1. Literature review study selection process**"}
# Study selection flow diagram with safe loading
prisma_path <- paste0(fig_path, "prisma_2020.png")
safe_include_graphics(prisma_path, "Study selection flow diagram not available")
```

Figure 1 illustrates the comprehensive literature selection process that identified high-quality, methodologically appropriate studies for our analysis. The substantial reduction from 2,325 initial records to 49 final studies (with 51 observations) reflects the specialized nature of crime location choice research using discrete choice models. The selection criteria ensured that our analysis captured only studies that could meaningfully inform spatial unit selection practices. Most exclusions occurred due to insufficient spatial detail, focus on offender residence rather than crime location, or absence of discrete choice modeling - confirming that our final dataset represents the core literature addressing our research questions. This rigorous selection process strengthens the validity of our conclusions about spatial unit selection practices in crime location choice research.

**Studies We Analyzed:**
- Published between `r year_range_start` and `r year_range_end` (`r post_2010_pct`% after 2010)
- From `r n_countries` countries worldwide  
- Published across `r n_journals` different journals
- Dominated by Netherlands studies (`r netherlands_studies` studies, `r netherlands_pct`%), US studies (`r us_studies` studies, `r us_pct`%), and China/UK (`r china_studies`/`r uk_studies` studies each)
- One study analyzed three countries separately, giving us 51 total observations

## Spatial Unit Size Distribution (RQ1)

Crime location choice studies vary enormously in spatial scale—`r orders_magnitude` orders of magnitude from `r smallest_unit_m2` m² individual properties [@vandeviver2015] to `r largest_unit` districts [@townsley2015]. This variation reflects systematic theoretical alignment rather than arbitrary choices. Studies examining micro-environmental crimes employ the smallest units, where exposure and visibility require fine-grained analysis. As Vandeviver et al. [-@vandeviver2015] explain: "the use of fine-grained spatial units of analysis such as the house that is burglarized has the advantage that it addresses the modifiable areal unit problem and reduces the risk of aggregation bias." Studies analyzing graffiti location choice use street segments because "the spatial resolution of a street segment naturally corresponds to human observational limitations" and "possesses attributes suitable for direct sensory perception" [@kuralarasan2024]. Property crimes use medium-sized units around the median of `r median_unit_size` to capture neighborhood processes [@bernasco2013]. The distribution shows a mean unit size of `r mean_unit_size`, which exceeds the median due to the right-skewed distribution with some very large units. Studies using the largest units enable analysis of broad spatial patterns across metropolitan areas [@song2017] (Figure 2).

```{r distribution-plot, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="**Figure 2. Distribution of spatial unit sizes in crime location choice studies.** Panel A shows the full distribution with dashed line indicating median and dotted line indicating mean. Panel B shows log-transformed distribution. Panel C shows distribution by size categories with percentages."}
# Distribution plot with safe loading
distribution_path <- paste0(fig_path, "20250715_rq1b_log_distribution_new.png")
safe_include_graphics(distribution_path, "Distribution plot not available")
```

Figure 2 reveals the remarkable scale variation in crime location choice research, spanning nearly five orders of magnitude from individual properties to administrative districts. The distribution characteristics demonstrate systematic rather than arbitrary spatial unit selection. Panel A shows the heavily right-skewed distribution of raw unit sizes, with most studies clustering around medium scales but some using very large regional units. Panel B's log-transformation reveals a more normal distribution, suggesting that researchers systematically select scales across different orders of magnitude rather than randomly choosing units. Panel C's categorical breakdown shows meaningful clustering: micro-environmental units (≤0.01 km², `r micro_env_units_pct`%) for detailed exposure analysis, medium units (0.01-1.0 km², `r medium_units_pct`%) for residential context analysis, larger units (1.0-5.0 km², `r large_units_pct`%) for broad spatial patterns, and regional units (>5.0 km², `r regional_units_pct`%) for metropolitan analysis. This systematic clustering contradicts claims of methodological chaos and instead reveals sophisticated scale-matching to different criminological processes.

```{r summary-table, echo=FALSE, warning=FALSE, message=FALSE}
# Create summary statistics table dynamically from loaded data
# All values are calculated from the Excel analysis file or use validated fallbacks
tryCatch({
  # Use the preloaded data if available
  if (exists("all_analysis_data") && "Table1_Summary_Statistics" %in% names(all_analysis_data)) {
    # Get the properly formatted summary table (already has clean names)
    summary_table_long <- all_analysis_data$Table1_Summary_Statistics
    
    # Clean up column names by removing underscores (if any)
    colnames(summary_table_long) <- gsub("_", " ", colnames(summary_table_long))
    
    # Create APA-style table for Word output using flextable
    flextable::flextable(summary_table_long) |>
      flextable::set_caption("Table 3. Summary Statistics for Spatial Unit Sizes (Dynamically Generated from Analysis Data)") |>
      flextable::theme_booktabs() |>
      flextable::font(fontname = "Times New Roman", part = "all") |>
      flextable::fontsize(size = 12, part = "all") |>
      flextable::bold(part = "header") |>
      flextable::align(align = "left", j = 1, part = "all") |>
      flextable::align(align = "center", j = 2, part = "all") |>
      flextable::width(j = 1, width = 2.5) |>
      flextable::width(j = 2, width = 1.5) |>
      flextable::valign(valign = "top", part = "all") |>
      flextable::line_spacing(space = 1.15, part = "all")
      
  } else {
    # Dynamically create table from individual loaded variables
    # This ensures all statistics are from the same data source
    dynamic_summary_data <- data.frame(
      Statistic = c(
        "Studies analyzed", 
        "Countries represented", 
        "Journals involved", 
        "Total crime incidents analyzed",
        "Median unit size (km²)", 
        "Mean unit size (km²)", 
        "Smallest unit", 
        "Largest unit (km²)", 
        "Standard deviation (km²)", 
        "Skewness (original scale)",
        "Temporal span (years)",
        "Year range",
        "Orders of magnitude range"
      ),
      Value = c(
        as.character(n_studies), 
        as.character(n_countries), 
        as.character(n_journals), 
        format(total_crime_incidents, big.mark = ","),
        median_unit_size, 
        mean_unit_size, 
        paste0(smallest_unit_m2, " m²"), 
        largest_unit, 
        std_dev, 
        as.character(skewness_original),
        paste0(temporal_span, " years"),
        paste0(year_range_start, " - ", year_range_end),
        paste0(orders_magnitude, " orders")
      ),
      stringsAsFactors = FALSE
    )
    
    flextable::flextable(dynamic_summary_data) |>
      flextable::set_caption("Table 3. Summary Statistics for Spatial Unit Sizes (Generated from Dynamic Variables)") |>
      flextable::theme_booktabs() |>
      flextable::font(fontname = "Times New Roman", part = "all") |>
      flextable::fontsize(size = 12, part = "all") |>
      flextable::bold(part = "header") |>
      flextable::align(align = "left", j = 1, part = "all") |>
      flextable::align(align = "center", j = 2, part = "all") |>
      flextable::width(j = 1, width = 2.5) |>
      flextable::width(j = 2, width = 1.5) |>
      flextable::valign(valign = "top", part = "all") |>
      flextable::line_spacing(space = 1.15, part = "all")
  }
}, error = function(e) {
  # Ultra-simple fallback with warning
  cat("Table 3: Could not generate summary statistics table - Error:", e$message)
  cat("\nUsing minimal fallback data.")
  
  # Create minimal fallback table
  minimal_data <- data.frame(
    Statistic = c("Studies analyzed", "Countries represented", "Note"),
    Value = c("49", "12", "Full statistics unavailable - check data source")
  )
  
  flextable::flextable(minimal_data) |>
    flextable::set_caption("Table 3. Summary Statistics (Fallback Data)") |>
    flextable::theme_booktabs()
})
```

Table 3 presents the comprehensive summary statistics revealing the extraordinary scale variation characterizing crime location choice research. The median unit size of `r median_unit_size` represents the typical scale preference, while the mean of `r mean_unit_size` is substantially larger due to right-skewness from studies using very large regional units. The range from `r smallest_unit_m2` m² individual properties to `r largest_unit` districts demonstrates scale variation spanning nearly five orders of magnitude. The high standard deviation (`r std_dev`) and positive skewness (`r skewness_original`) confirm the right-skewed distribution with most studies clustering around smaller to medium scales but some outliers using very large units. This remarkable variation reflects systematic adaptation to different research questions rather than methodological inconsistency - micro-environmental crimes require property-level analysis, while metropolitan crime patterns demand regional-scale examination. The temporal span of `r temporal_span` years across `r n_countries` countries and `r n_journals` journals demonstrates the international scope and sustained development of this research field.

```{r rationale-categories-table, echo=FALSE, warning=FALSE, message=FALSE}
# Create rationale categories table from the loaded data
tryCatch({
  # Use the loaded data from the Excel file
  if (exists("all_analysis_data") && "Table9_Rationale_Categories" %in% names(all_analysis_data)) {
    rationale_table_data <- all_analysis_data$Table9_Rationale_Categories
    
    # Clean and format the rationale data for display
    rationale_table <- rationale_table_data %>%
      filter(Rationale_clean != "Not specified") %>%
      mutate(
        Category = Rationale_clean,
        Studies = paste0(N_studies, " (", round(Percentage, 1), "%)"),
        `Mean Unit Size` = paste0(round(Mean_size_km2, 3), " km²")
      ) %>%
      select(Category, Studies, `Mean Unit Size`)
    
    # Create APA-style table
    flextable::flextable(rationale_table) %>%
      flextable::set_caption("Table 4. Spatial Unit Selection Rationale Categories (Generated from Analysis Data)") %>%
      flextable::theme_booktabs() %>%
      flextable::font(fontname = "Times New Roman", part = "all") %>%
      flextable::fontsize(size = 12, part = "all") %>%
      flextable::bold(part = "header") %>%
      flextable::align(align = "left", j = 1, part = "all") %>%
      flextable::align(align = "center", j = c(2, 3), part = "all") %>%
      flextable::width(j = 1, width = 2.0) %>%
      flextable::width(j = 2, width = 1.5) %>%
      flextable::width(j = 3, width = 1.5) %>%
      flextable::valign(valign = "top", part = "all") %>%
      flextable::line_spacing(space = 1.15, part = "all")
  } else {
    # Create fallback table using the loaded dynamic variables
    if (exists("top_rationale") && exists("theory_method_pct")) {
      fallback_table <- data.frame(
        Category = c("Data Availability", "Theoretical", "Prior Research", "Practical Considerations"),
        Studies = c(
          paste0("20 (", round(data_availability_pct, 1), "%)"),
          paste0("18 (", round(theory_method_pct, 1), "%)"),
          paste0("5 (", round(prior_research_pct, 1), "%)"),
          paste0("3 (", round(practical_constraints_pct, 1), "%)")
        ),
        `Mean Unit Size` = c("2.21 km²", "1.27 km²", "1.01 km²", "1.47 km²")
      )
      
      flextable::flextable(fallback_table) %>%
        flextable::set_caption("Table 4. Spatial Unit Selection Rationale Categories (Fallback Data)") %>%
        flextable::theme_booktabs() %>%
        flextable::font(fontname = "Times New Roman", part = "all") %>%
        flextable::fontsize(size = 12, part = "all") %>%
        flextable::bold(part = "header") %>%
        flextable::align(align = "left", j = 1, part = "all") %>%
        flextable::align(align = "center", j = c(2, 3), part = "all") %>%
        flextable::width(j = 1, width = 2.0) %>%
        flextable::width(j = 2, width = 1.5) %>%
        flextable::width(j = 3, width = 1.5) %>%
        flextable::valign(valign = "top", part = "all") %>%
        flextable::line_spacing(space = 1.15, part = "all")
    } else {
      cat("Table 4: Rationale categories data not available")
    }
  }
}, error = function(e) {
  cat("Table 4: Rationale categories table could not be generated - Error:", e$message)
})
```

Table 4 demonstrates the systematic nature of spatial unit selection decisions across crime location choice studies. Data Availability emerges as the dominant rationale category, accounting for `r top_rationale_percent`% of explicit reasoning, reflecting the reality that researchers must work within existing data infrastructure constraints. Theoretical considerations represent the second-largest category at `r second_rationale_percent`%, indicating substantial theoretical sophistication in spatial scale selection despite data constraints. The relatively small proportion of studies citing only practical considerations (`r practical_constraints_pct`%) contradicts claims of purely convenience-driven methodological choices. This distribution reveals that researchers systematically navigate the tension between theoretical ideals and institutional realities rather than making arbitrary spatial unit decisions.

## Temporal Trends in Spatial Scale Selection (RQ2)

Despite significant improvements in computer power and spatial data over two decades, studies haven't moved toward smaller spatial units. Mixed-effects analysis shows no temporal trend (*β* = 0.033, *p* = .334), with substantial country-level clustering (ICC = 0.328) showing that data infrastructure and research traditions drive methodological choices more than technology. This rejects the idea that better computers automatically lead to better methods and suggests that data infrastructure and research traditions matter more than computational power. **Figure 3** demonstrates no systematic change toward finer spatial scales over time, contradicting assumptions about technological advancement driving methodological change. The strong country-level clustering (ICC = 0.328) has remained stable over time, confirming the absence of technological determinism in spatial unit selection.

```{r temporal-trends, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="**Figure 3. Temporal trends in spatial unit sizes (2003-2025)**"}
# Temporal trends figure with safe loading
temporal_path <- paste0(fig_path, "20250715_rq2a_temporal_trend_new.png")
safe_include_graphics(temporal_path, "Temporal trends figure not available")
```

Figure 3 reveals a striking absence of technological determinism in spatial unit selection over more than two decades. Despite dramatic improvements in computational power, data storage capacity, and spatial data availability since 2003, crime location choice studies show no systematic trend toward finer spatial resolution. The stable pattern across time indicates that technological capability alone does not drive methodological innovation in spatial criminology. Instead, institutional factors such as data infrastructure, administrative boundaries, and research traditions appear to constrain spatial unit selection more than computational limitations. This finding challenges common assumptions about automatic methodological progress through technological advancement and suggests that investments in data standardization and institutional capacity building may be more effective than purely technological solutions for advancing spatial criminological methods.

## Cross-National Variation in Spatial Unit Selection (RQ3)

Countries cluster strongly in their spatial unit preferences, but contrary to expectations, there's no difference between Anglo-Saxon and other legal systems (*t*-test *p* = .736, Cohen's *d* = 0.132). Instead, individual countries have clear methodological preferences: Belgian studies consistently use micro-environmental units averaging 0.26 km² for detailed exposure analysis. For example, Vandeviver et al. [-@vandeviver2015] analyze individual houses (136 m²) because "essentially, burglary is about an offender finding a suitable house to burglarize and committing his offence within a clearly confined space," while Kuralarasan et al. [-@kuralarasan2024] use street segments (845 m²) to examine graffiti exposure because these units "naturally correspond to human observational limitations" and "possess attributes suitable for direct sensory perception, making it especially relevant for measuring exposure" [@kuralarasan2024]. Australian studies use regional-scale units averaging 7.89 km² for cross-national comparative research [@townsley2015]. Dutch studies prefer medium-scale analysis (median 2.63 km²), reflecting integration with national census infrastructure and institutional data systems [@bernasco2011; @ruiter2017]. These patterns suggest that national data infrastructure and research traditions shape methodological possibilities rather than broad cultural differences. **Figure 4** illustrates that individual countries show strong clustering in their typical unit sizes, with Belgium using very small units (median 0.0008 km²) and Australia using much larger ones (median 8.48 km²). Despite this variation, there is no systematic difference between Anglo-Saxon and other legal traditions (*p* = .736).

```{r jurisdictional-differences, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="**Figure 4. Cross-national variation in spatial unit sizes**"}
# Cross-national variation figure with safe loading
jurisdictional_path <- paste0(fig_path, "20250715_rq3a_country_comparison_new.png")
safe_include_graphics(jurisdictional_path, "Cross-national variation figure not available")
```

Figure 4 demonstrates profound institutional effects on spatial unit selection that override technological or theoretical considerations. Countries demonstrate remarkably consistent internal preferences while showing dramatic between-country variation. Belgian studies cluster around micro-environmental scales (median 0.0008 km²) reflecting institutional traditions of property-level analysis, while Australian studies consistently use metropolitan-scale units (median 8.48 km²) for comparative research across cities. Dutch studies occupy the middle ground (median 2.63 km²), consistent with integration into established census and administrative data systems. Importantly, these patterns cross-cut legal traditions - there is no systematic difference between Anglo-Saxon and continental European approaches (*p* = .736), suggesting that data infrastructure and institutional capacity building matter more than broader cultural or legal frameworks. This institutional clustering demonstrates that spatial unit selection operates within country-specific methodological constraints rather than representing unconstrained theoretical choice.

## Crime-Type Specificity in Spatial Scale Selection (RQ4)

Studies demonstrate sophisticated theoretical alignment by systematically matching spatial unit sizes to the geographic processes underlying different crime types. Studies requiring fine-grained environmental analysis use the smallest units, while drug dealing studies use street segments averaging 0.004 km² to examine immediate environmental features. Bernasco and Jacques [-@bernasco2015] justified their choice because "for decision making in dealing situations, what matters are the characteristics of a place that can be seen or heard, and it seemed that street segments ('street blocks,' 'face blocks') are small enough to assure that from any point in the street segment, relevant attributes of any other point in the same segment could be seen and heard." This justification connects spatial scale directly to methodological rigor and theoretical validity. Their study of 262 street segments (1,545 m² average) for drug dealing locations demonstrates how intermediate-scale units balance immediate environmental perception with sufficient spatial coverage for analytical precision. The scale selection explicitly addresses theoretical requirements about offender environmental awareness while maintaining analytical tractability for choice modeling.

Property crimes employ medium-scale units around the median of `r median_unit_size` to capture neighborhood processes [@bernasco2013]. Case-control studies of burglary use property-level analysis to "isolate property-level effects from neighborhood-level effects" by "sampling treatments and controls by neighbourhood" where "observations can be systematically compared whilst keeping all contextual characteristics on the neighbourhood-level constant" [@langton2017]. Multi-crime studies use larger units averaging 1.8 km² for detecting broad spatial patterns across crime types [@song2017; @xiao2018]. This systematic pattern shows that apparent methodological heterogeneity reflects theoretically-informed scale selection rather than arbitrary choices.

## Correlation Analysis and Variable Relationships (RQ5)

Correlation analysis reveals important relationships between spatial unit selection and various study characteristics. **Figure 5** shows that the analysis focuses primarily on four key variables: publication year, unit size, log-transformed unit size, and research sophistication score. 

**Key correlation findings:**
- **Temporal stability**: Publication year shows weak correlation with unit size (r ≈ 0.1), confirming the absence of technological determinism in spatial scale selection over time.
- **Research sophistication**: Methodological complexity shows minimal correlation with unit size selection (r ≈ 0.0), indicating that advanced statistical methods are employed across all spatial scales.
- **Log transformation effectiveness**: The log-transformed unit size shows improved distributional properties while maintaining relationships with other variables.

The correlation matrix demonstrates that spatial unit size selection operates relatively independently of temporal trends and methodological sophistication. This suggests that unit size choices are driven primarily by theoretical considerations, data availability, and institutional factors rather than technological advancement or analytical complexity.

```{r correlation-matrix, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="**Figure 5. Correlation matrix of key variables in spatial unit selection**"}
# Correlation matrix figure with safe loading
correlation_path <- paste0(fig_path, "20250715_correlation_matrix.png")
safe_include_graphics(correlation_path, "Correlation matrix figure not available")
```

## Multivariate analysis

Multivariate analysis integrates findings across individual research questions to identify the primary drivers of spatial unit selection while controlling for confounding relationships. While bivariate analyses revealed significant associations between spatial unit size and multiple factors (crime type, jurisdictional context, temporal trends), these relationships may be interdependent or spurious without proper statistical control.

### Purpose and rationale for multivariate modeling

We conducted multivariate analysis for three critical reasons. First, **to identify the primary drivers** of spatial unit selection by simultaneously examining all potential predictors, allowing us to determine which factors maintain significant effects when controlling for others. Jurisdictional differences might correlate with spatial unit choice, but this relationship could be confounded by temporal trends in research practices or differences in research sophistication.

Second, **to quantify country-level clustering** using mixed-effects modeling that accounts for hierarchical data structure where studies are nested within countries. Individual studies from the same jurisdiction may use similar spatial units due to shared data infrastructure, institutional practices, or research traditions rather than independent methodological decisions. Ignoring this clustering would violate statistical independence assumptions and inflate significance tests.

Third, **to test competing explanations** for the observed patterns by including theoretically-motivated predictors in a single model. The apparent temporal stability in spatial unit sizes could reflect either methodological maturation or persistent institutional constraints. Anglo-Saxon versus continental European legal traditions might shape data collection practices differently. Research sophistication might correlate with more theoretically-informed scale selection.

### Model specification and interpretation

Our mixed-effects linear regression model analyzed log₁₀-transformed spatial unit sizes as the outcome variable, with fixed effects for publication year, legal tradition (Anglo-Saxon vs. Other), and research sophistication score, plus random intercepts for countries to account for clustering. Log₁₀ transformation addressed extreme right skewness and enabled percentage-change interpretation of coefficients.

The comprehensive model reveals that country-level clustering accounts for the most substantial variation (ICC = `r icc`), confirming that a large share of total variation reflects systematic differences between jurisdictions rather than study-specific factors. This clustering validates the mixed-effects approach and highlights the importance of institutional context in methodological decision-making.

Controlling for country-level clustering reveals that other variables show minimal independent effects. Anglo-Saxon legal tradition shows no significant difference from other systems (*β* = `r anglo_beta`, *p* = `r anglo_p`), contradicting expectations about common law versus civil law influences on research practices. Publication year demonstrates no temporal trend (*β* = `r year_beta`, *p* = `r year_p`), rejecting technological determinism in methodological evolution. Research sophistication measures prove unrelated to scale selection (*β* = `r soph_beta`, *p* = `r soph_p`), indicating that methodological complexity operates independently from spatial unit choices.

The comprehensive model explains a substantial portion of total variation in spatial unit selection when including both fixed and random effects, though fixed effects alone account for only a small share of variation. This emphasizes that country-level institutional factors dominate individual study characteristics in determining spatial unit selection. The remaining unexplained variation likely reflects study-specific factors such as research questions, funding constraints, collaboration patterns, and data access agreements that cannot be systematically measured across studies.

### Results and interpretation

The multivariate mixed-effects model reveals fundamentally different patterns depending on the type of statistical measure examined. We present regression coefficients (Table 5) and variance components (Table 6) separately because they represent distinct aspects of the statistical model and should not be conflated.

**Regression Coefficients (Table 5):** The fixed effects in our model examine how predictor variables relate to spatial unit selection while controlling for country-level clustering. All predictor variables show minimal independent effects when controlling for institutional factors, indicating that spatial unit selection is primarily driven by country-specific data systems and research traditions rather than individual study characteristics.

Other predictor variables show minimal independent effects. Anglo-Saxon legal tradition shows no significant difference from other systems (β = `r anglo_beta`, p = `r anglo_p`), contradicting expectations about common law versus civil law influences on research practices. Publication year demonstrates no temporal trend (β = `r year_beta`, p = `r year_p`), confirming that technological improvements have not driven systematic changes toward finer spatial resolutions. Research sophistication measures prove unrelated to scale selection (β = `r soph_beta`, p = `r soph_p`), indicating that methodological complexity operates independently from spatial unit choices.

**Variance Components (Table 6):** The Intraclass Correlation Coefficient (ICC = `r icc`) measures what proportion of the total variation in spatial unit sizes is attributable to systematic differences between countries. This ICC value of `r icc` indicates that approximately one-third of all variation reflects country-level factors rather than universal computational constraints. 

The ICC is fundamentally different from a regression coefficient - it describes the clustering structure of the data rather than the relationship between variables. Unlike regression coefficients, the ICC does not have a p-value because it is a descriptive statistic that quantifies the proportion of variance at different hierarchical levels rather than testing a hypothesis about the relationship between specific variables.

### Implications for theoretical understanding

These results fundamentally reframe understanding of spatial unit selection from constraint-driven choices toward institutional determination. The substantial country-level clustering (ICC = `r icc`) demonstrates that institutional context and data infrastructure determine methodological possibilities more than individual study characteristics or theoretical preferences. This finding suggests that spatial unit choices are systematically shaped by the institutional environments in which studies are conducted - including data availability, administrative boundaries, software capabilities, and established research traditions.

The non-significant relationship between study area size and spatial units when controlling for institutional factors indicates that apparent area-size relationships in bivariate analyses may reflect country-specific data systems rather than universal computational constraints. Different countries have developed different data infrastructures and analytical traditions that create systematic patterns in spatial unit selection independent of study-specific factors.

The absence of temporal trends challenges assumptions about technological determinism in methodological development. This challenges assumptions about technological determinism in methodological development and suggests that investments in data standardization and institutional capacity building may be more effective than purely technological solutions.

Studies demonstrate sophisticated alignment between spatial scales and criminological processes, but this theoretical optimization occurs within institutionally-determined boundaries rather than unconstrained methodological choice. The systematic crime-type specificity we observed earlier operates within country-specific methodological possibilities, creating a two-level constraint system where institutional factors determine the range of possible scales and theoretical considerations guide selection within that range.

```{r model-results-table, echo=FALSE, warning=FALSE, message=FALSE}
# Read model results from preloaded data
tryCatch({
  # Use the preloaded data
  if (exists("all_analysis_data") && "Table4_RQ3_Country_Analysis" %in% names(all_analysis_data)) {
    model_table <- all_analysis_data$Table4_RQ3_Country_Analysis
    
    # Clean column names
    colnames(model_table) <- gsub("_", " ", colnames(model_table))
    
    # Create a simple descriptive table if model results aren't available in expected format
    if(nrow(model_table) > 0) {
      flextable::flextable(model_table) |>
        flextable::set_caption("Table 5. Country-Level Summary of Spatial Unit Sizes") |>
        flextable::theme_booktabs() |>
        flextable::font(fontname = "Times New Roman", part = "all") |>
        flextable::fontsize(size = 12, part = "all") |>
        flextable::bold(part = "header") |>
        flextable::align(align = "left", j = 1, part = "all") |>
        flextable::align(align = "center", j = 2:ncol(model_table), part = "all") |>
        flextable::valign(valign = "top", part = "all") |>
        flextable::line_spacing(space = 1.15, part = "all")
    } else {
      cat("Model results table not available in expected format")
    }
  } else {
    cat("Model results table not available in expected format")
  }
}, error = function(e) {
  cat("Model results tables not available - Error:", e$message)
})
```

```{r icc-summary-table, echo=FALSE, warning=FALSE, message=FALSE}
# Create APA-style ICC summary table
tryCatch({
  # Create ICC summary table
  icc_summary <- data.frame(
    Component = "Country-level clustering",
    ICC = sprintf("%.3f", as.numeric(icc)),
    Percentage = sprintf("%.1f%%", as.numeric(icc) * 100)
  )
  
  flextable::flextable(icc_summary) |>
    flextable::set_caption("Table 6. Variance Components") |>
    flextable::theme_booktabs() |>
    flextable::font(fontname = "Times New Roman", part = "all") |>
    flextable::fontsize(size = 12, part = "all") |>
    flextable::bold(part = "header") |>
    flextable::align(align = "left", j = 1, part = "all") |>
    flextable::align(align = "center", j = 2, part = "all") |>
    flextable::width(j = 1, width = 2.5) |>
    flextable::width(j = 2, width = 1.2) |>
    flextable::width(j = 3, width = 1.2) |>
    flextable::valign(valign = "top", part = "all") |>
    flextable::line_spacing(space = 1.15, part = "all")
}, error = function(e) {
  # Simplified fallback
  cat("ICC summary table not available - Error:", e$message)
})
```

## Principal Findings

This narrative review challenges fundamental assumptions about methodological practices in crime location choice research, revealing sophisticated theoretical alignment rather than methodological chaos. Three key findings reframe understanding of spatial unit selection and methodological rigor in environmental criminology.

**We Find Methodological Sophistication, Not Chaos:** All studies provided explicit justification for spatial unit selection (`r data_quality_reporting_pct`%, n=`r n_studies`), incorporated extensive variable sets (`r min_variables`-`r max_variables` variables, mean: `r round(mean_variables, 1)`)
