---
title: "Test Document - Methods Section"
output: 
  word_document:
    reference_docx: "reference.docx"
    fig_caption: true
    df_print: kable
bibliography: references.bib
csl: https://www.zotero.org/styles/apa
link-citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = "figures/",
  dpi = 300
)

# Load required libraries
library(knitr)
library(kableExtra)
library(flextable)
library(officer)
library(readxl)
library(tidyverse)

# Set figure and table paths
fig_path <- "20250712_Analysis & Results/"
table_path <- "20250712_Analysis & Results/Manuscript_All_Tables.xlsx"

# Load model results for inline referencing throughout document
# Define variables with values from latest R analysis results
naive_search_total <- 249
total_records_identified <- 2325
```

# Methods

## Study Design and Registration

We conducted a systematic scoping review following the Preferred Reporting Items for Systematic Reviews and Meta-Analyses Extension for Scoping Reviews (PRISMA-ScR) guidelines [@tricco2018]. The review protocol was developed based on established frameworks for conducting systematic scoping reviews [@arksey2005; @guidance2023]. No protocol was pre-registered due to the exploratory nature of the research questions.

## Search Strategy

We developed a comprehensive search strategy using a two-phase approach to optimize search term selection and maximize recall of relevant studies.

### Phase 1: Initial Search and Keyword Extraction

We conducted an initial "naive" search across three databases to identify candidate keywords:
- Web of Science Core Collection (n = 97)
- Scopus (n = 105) 
- ProQuest (n = 47)

The naive search strategy employed broad Boolean terms across three conceptual domains (population, intervention, outcome) to capture studies analyzing offender location choice decisions through discrete choice models:

```{r naive-search-table, echo=FALSE, warning=FALSE, message=FALSE}
# Create table for naive search terms
naive_search_terms <- data.frame(
  Database = c("Web of Science", "Scopus", "ProQuest"),
  `Search String` = c(
    "TS=(((offend* OR crim* OR burglar* OR robb* OR co-offend* OR dealer*) AND (\"discret* choic*\" OR \"choic* model*\" OR \"rational choice\" OR \"awareness space\" OR \"journey to crime\" OR \"mobility\" OR \"opportunity\" OR \"accessibility\" OR \"attractiveness\" OR \"crime pattern*\") AND (\"crime locat* choic*\" OR \"offend* locat* choic*\" OR \"robber* locat* choic*\" OR \"burglar* locat* choic*\" OR \"target area*\" OR \"target selection\" OR \"crime site selection\" OR \"spatial choic* model*\")))",
    "TITLE-ABS-KEY(((offend* OR crim* OR burglar* OR robb* OR co-offend* OR dealer*) AND (\"discret* choic*\" OR \"choic* model*\" OR \"rational choice\" OR \"awareness space\" OR \"journey to crime\" OR \"mobility\" OR \"opportunity\" OR \"accessibility\" OR \"attractiveness\" OR \"crime pattern*\") AND (\"crime locat* choic*\" OR \"offend* locat* choic*\" OR \"robber* locat* choic*\" OR \"burglar* locat* choic*\" OR \"target area*\" OR \"target selection\" OR \"crime site selection\" OR \"spatial choic* model*\")))",
    "noft(((offend* OR crim* OR burglar* OR robb* OR co-offend* OR dealer*) AND (\"discret* choic*\" OR \"choic* model*\" OR \"rational choice\" OR \"awareness space\" OR \"journey to crime\" OR \"mobility\" OR \"opportunity\" OR \"accessibility\" OR \"attractiveness\" OR \"crime pattern*\") AND (\"crime locat* choic*\" OR \"offend* locat* choic*\" OR \"robber* locat* choic*\" OR \"burglar* locat* choic*\" OR \"target area*\" OR \"target selection\" OR \"crime site selection\" OR \"spatial choic* model*\")))"
  ),
  Records = c("97", "105", "47")
)

# Create formatted table
naive_table <- flextable(naive_search_terms) %>%
  set_caption("**Table 1. Naive search strategy and results**") %>%
  theme_vanilla() %>%
  bold(part = "header") %>%
  font(fontname = "Times New Roman", part = "all") %>%
  autofit()

naive_table
```

This initial search used broad terms related to crime location choice, discrete choice modeling, and spatial analysis. The `r naive_search_total` initial results were deduplicated and used as input for systematic keyword extraction.

## Test Conclusion

This test document should render successfully to this point.
